On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-04 main.tex
changed sections/subsections

\section{Weak Transversality}

@@

@@

\subsection{Genericity and Sard's lemma}
It will sometimes be useful for us use in replace of the matrix $A$, a matrix representing indeterminants: let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ It follows from Proposition 5.1, that for a generic $A \in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of \cite[Theorem B.3]{TWT}, which establishes the existence of $\Delta \subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the critical values of a polynomial mapping are contained in a hypersurface. It follows from Sard's lemma that, for the matrix of indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise it could not be that $0$ is a regular value of $\Phi_A,$ for a generic $A\in \C^{n^2}.$ The proof is routine and we omit details. It then follows that 
\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(\xb),\frac{\pa f^{\A}(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(\xb)}{\pa X_n}\right)
has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}. We will rely on this fact in Section 8.
\section{Proof of $\textbf{H}_i'(1),\textbf{H}_i'(2)$ and $\textbf{H}_i'(3)$}
We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is squarefree with $V(f) \cap \mathbb{R}^n$ smooth. Thus, by Proposition 2.4,  $W(\pi_i,V(f))$ is defined by the vanishing of $f,\frac{\pa f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.$ If the Jacobian of this set of polynomials has full rank at all $\xb \in V(f) \cap \mathbb{R}^n,$ then it follows by the Jacobian criterion \cite[Theorem 16.19]{ECA} that $f$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$. 
There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
\subsection{Sketch of the proof of Theorem 4.1}
For each $i \in \{1,\hdots,n\}$, let $\Phi_i$ be the polynomial mapping 
\Phi_i : (\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $\bz$ is a regular value of $\Phi_i$, where then it follows that $\Xi_i \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Xi_i$ then  
\jac_{\xb}(\Phi_{i,A}) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)
has full rank at all $\xb \in V(f^A)~(\cap\R^n$?). Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$. To obtain the result for all $i \in \{1,\hdots,n\}$, we take 
\Delta_1 = \bigcup_{i=1}^n \Xi_i 
where we can bound the degree by observing that 
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i.
\subsection{Proof of Theorem 4.1}
Fix $i \in \{1,\hdots,n\}$, and let $\Phi_i$ be as stated above.
$\bz$ is a regular value of $\Phi_i$.
Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that 
$f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=\bz.$
We want to show that the Jacobian of the system of polynomials 
f(A\xb),(\grad(f)\cdot A_{i+1})(A\xb),\hdots, (\grad(f)\cdot A_n)(A\xb)
at $(\xb,A)$ has full rank, which holds if and only if the Jacobian of the system of polynomials 
f,\grad(f)\cdot A_{i+1},\hdots, \grad(f)\cdot A_n
at $(\xb,A)$ has full rank. Let $\Psi_i$ be the mapping
    \Psi_i: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
       (\xb,A) &\mapsto 
       \left(f(\xb),\grad(f(\xb))\cdot 
A_{i+1},\hdots
\grad(f(\xb))\cdot 
A_{n}
\right).
For all $(\xb,A) \in \Psi_i^{-1}(0),$ the Jacobian matrix of $\Psi_i$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, ~1 \leq j \leq n-i,
so that the Jacobian is equal to
\left[ 
\begin{array}{cccccc}
\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
\ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
\end{array}
\right]. 
Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes. At least one partial of $f$ must be non-zero. Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
Since $\deg \Phi_i \leq d,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $d^{n+(n-i+1)}=d^{2n-i+1}\leq d^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then 
 \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
\Delta_1 := \bigcup_{i=1}^n \Xi_i,
where we have the following bound on the degree which proves the claim:
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
\section{Proof of $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$}
There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of degree at most $\td$ with the property that, if $A \in \C^{n^2} - \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
\subsection{Sketch of the proof of Theorem 5.1}
Let $p_{n-1} = (\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
X_1(\xb)-\alpha_1,\hdots,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),  \frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}
has full rank, at all points $(\xb,A) \in \C^n \times \C^{n^2}$ in the zero set of this system. It would then follow from Theorem 5.1 that a hypersurface  exists with the desired properties. 
\subsection{Proof of Theorem 5.1}
Let $\Phi_i$ be the mapping 
    \Phi_i: \C^n \times \C^{i-1} &\rightarrow \C^{n} \\
           (\xb,\alpha_1,\hdots,\alpha_{i-1}) &\mapsto 
       (X_1(\xb)-\alpha_1,\hdots \\
       \hdots &,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),\frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n} ).
$\bz$ is a regular value of $\Phi_i.$
For all $(\xb,A) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ at $(\xb,A)$ has full rank $\td$. Indeed, the Jacobian is equal to
\left[ 
\begin{array}{cccccc}
\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
\ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
\end{array}
\right]. 
Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes. At least one partial of $f$ must be non-zero. Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then 
 \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
\Delta_1 := \bigcup_{i=1}^n \Xi_i,
where we have the following bound on the degree which proves the claim:
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq D^{2n^2}.
\section{Proof of $\textbf{H}_i'(7)$}
Let $\A$ be an $n \times n$ matrix of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in \mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$ Recall from Section 4.1.4 that $f^\A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$ Throughout this section, to simplify notation, let $\I^\A$ denote $\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore, throughout this section, consider that $i \in \{1,\hdots,n\}$ is fixed. We will avoid writing $i$ where the context is clear. 
\subsection{Sketch of the proof}
Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ have total degree $D$. Assume $f$ satisfies \textbf{H}, so that $f$ is squarefree with $V(f)$ smooth. Recall $\textbf{H}_i^{'}(7):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension  
%% >>>>>>> f9eb2445ca6e153d1e49c3d2767097d331dbcbee

>>>>

\section{Weak Transversality and Applications}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Weak Transversality}

@@

It will sometimes be useful for us use in replace of the matrix $A$, a
matrix representing indeterminants: let $\A$ be an $n \times n$ matrix
of new indeterminates $(\A_{i,j})_{1 \leq i , j \leq n}.$ Define
$f^{\A} \in \mathbb{Q}(\A_{i,j})[\textbf{X}]$ as $f(\A\textbf{X})$ and
$V^\A=V(f^\A).$ It follows from Proposition 5.1, that for a generic $A
\in \C^{n^2},$ $0$ is a regular value of $\Phi_{A}$.  The proof of
\cite[Theorem B.3]{TWT}, which establishes the existence of $\Delta
\subset \C^{n^2},$ applies \textit{Sard's lemma}, which shows that the
critical values of a polynomial mapping are contained in a
hypersurface. It follows from Sard's lemma that, for the matrix of
indeterminants $\A,$ $0$ is a regular value of $\Phi_{\A}.$ Otherwise
it could not be that $0$ is a regular value of $\Phi_A,$ for a generic
$A\in \C^{n^2}.$ The proof is routine and we omit details. It then
follows that
\[
\jac_{\xb}(\Phi_{\A}) = \jac_{\xb}\left(f^{\A}(\xb),\frac{\pa f^{\A}(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^{\A}(\xb)}{\pa X_n}\right)
\]
has full rank for all $\xb \in V(f^{\A})$, and thus $f^{\A}$satisfies
$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by
the Jacobian criterion \cite[Theorem 16.19]{ECA}. We will rely on this
fact in Section 8.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Application: property $\textbf{H}_i(1)$}

We assume our input polynomial $f$ satisfies \textbf{H} so that $f$ is
squarefree with $V(f) \cap \mathbb{R}^n$ smooth. Thus, by Proposition
2.4, $W(\pi_i,V(f))$ is defined by the vanishing of $f,\frac{\pa
  f}{\pa X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.$ If the Jacobian of
this set of polynomials has full rank at all $\xb \in V(f) \cap
\mathbb{R}^n,$ then it follows by the Jacobian criterion \cite[Theorem
  16.19]{ECA} that $f$ satisfies
$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
%
\begin{theorem}
There exists a Zariski closed set $\Delta_1 \subset \C^{n^2}$ of degree at most $d^{2n^2}$ with the property that, if $A \in \C^{n^2} - \Delta_1$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$.
\end{theorem}

For each $i \in \{1,\hdots,n\}$, let $\Phi_i$ be the polynomial mapping 
\[
\Phi_i : (\xb,A) \mapsto \left(f^A(\xb), \frac{\partial f^A}{\partial X_{i+1}}(\xb),\hdots,\frac{\partial f^A}{\partial X_n}(\xb)\right),
\] 
so that $\Phi_{i,A}^{-1}(0)= W(\pi_i,V^A).$ We want to apply Theorem 5.1, and thus we show that $\bz$ is a regular value of $\Phi_i$, where then it follows that $\Xi_i \subset \C^{n^2}$ exists with the property that if $A \in \C^{n^2}-\Xi_i$ then  
\[
\jac_{\xb}(\Phi_{i,A}) = \jac_{\xb}\left(f^A(\xb),\frac{\pa f^A(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f^A(\xb)}{\pa X_n}\right)
\]
has full rank at all $\xb \in V(f^A)~(\cap\R^n$?). Then, by the Jacobian criterion \cite[Theorem 16.19]{ECA}, $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$. To obtain the result for all $i \in \{1,\hdots,n\}$, we take 
\[
\Delta_1 = \bigcup_{i=1}^n \Xi_i 
\]
where we can bound the degree by observing that 
\[
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i.
\]

Fix $i \in \{1,\hdots,n\}$, and let $\Phi_i$ be as stated above.
%
\begin{proposition} 
$\bz$ is a regular value of $\Phi_i$.
\end{proposition}
%
\begin{proof}
Let $A_1,\hdots,A_n$ denote the columns of $A,$ and let $(\xb,A) \in \C^n \times \C^{n^2}$ be such that 
$f^A(\xb) = \frac{\partial f^A(\xb)}{\partial X_{i+1}}=\hdots= \frac{\partial f^A(\xb)}{\partial X_n}=\bz.$
We want to show that the Jacobian of the system of polynomials 
\[
f(A\xb),(\grad(f)\cdot A_{i+1})(A\xb),\hdots, (\grad(f)\cdot A_n)(A\xb)
\]
at $(\xb,A)$ has full rank, which holds if and only if the Jacobian of the system of polynomials 
\[
f,\grad(f)\cdot A_{i+1},\hdots, \grad(f)\cdot A_n
\]
at $(\xb,A)$ has full rank. Let $\Psi_i$ be the mapping
%
\begin{align*}
    \Psi_i: \C^n \times \C^{n^2} &\rightarrow \C^{n-i+1} \\
       (\xb,A) &\mapsto 
       \left(f(\xb),\grad(f(\xb))\cdot 
A_{i+1},\hdots
\grad(f(\xb))\cdot 
A_{n}
\right).
\end{align*}
%
For all $(\xb,A) \in \Psi_i^{-1}(0),$ the Jacobian matrix of $\Psi_i$ at $(\xb,A)$ has full rank $n-i+1$. Indeed, set 
\[
F_j = \frac{\pa f}{\pa X_1} a_{i+j,1} + \hdots + \frac{\pa f}{\pa X_n}a_{i+j,n}, ~1 \leq j \leq n-i,
\]
so that the Jacobian is equal to
\[
\left[ 
\begin{array}{cccccc}
\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
\frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
\ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
\frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
\end{array}
\right]. 
\] 
Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
\[
T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
\]
Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes. At least one partial of $f$ must be non-zero. Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
\end{proof}
%
Since $\deg \Phi_i \leq d,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $d^{n+(n-i+1)}=d^{2n-i+1}\leq d^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then 
%
\[
 \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
\]
has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
\[
\Delta_1 := \bigcup_{i=1}^n \Xi_i,
\]
where we have the following bound on the degree which proves the claim:
\[
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq d^{2n^2}.
\]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Application: property $\textbf{H}'_i$}

\begin{theorem}
  There exists a Zariski closed set $\Delta_2 \subset \C^{n^2}$ of
  degree at most $\td$ with the property that, if $A \in \C^{n^2} -
  \Delta_2$ then for each $i \in \{1,\hdots,n\},$ $f^A$ satisfies
  $\textbf{H}_i'(4),\textbf{H}_i'(5)$ and $\textbf{H}_i'(6)$.
\end{theorem}

Let $p_{n-1} = (\alpha_1,\hdots,\alpha_{n-1}) \in \Q^{n-1}$ be a randomly chosen point. For $i \in \{1,\hdots,n\}$, we want to show that the Jacobian of the system of polynomials
\[
X_1(\xb)-\alpha_1,\hdots,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),  \frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n}
\]
has full rank, at all points $(\xb,A) \in \C^n \times \C^{n^2}$ in the zero set of this system. It would then follow from Theorem 5.1 that a hypersurface  exists with the desired properties.

Let $\Phi_i$ be the mapping 
%
\begin{align*}
    \Phi_i: \C^n \times \C^{i-1} &\rightarrow \C^{n} \\
           (\xb,\alpha_1,\hdots,\alpha_{i-1}) &\mapsto 
       (X_1(\xb)-\alpha_1,\hdots \\
       \hdots &,X_{i-1}(\xb)-\alpha_{i-1}, f(\xb),\frac{\pa f(\xb)}{\pa X_{i+1}},\hdots,\frac{\pa f(\xb)}{\pa X_n} ).
\end{align*}
%
\begin{proposition}
$\bz$ is a regular value of $\Phi_i.$
\end{proposition} 
\begin{proof}
For all $(\xb,A) \in \Phi_i^{-1}(0),$ the Jacobian matrix of $\Phi_i$ at $(\xb,A)$ has full rank $\td$. Indeed, the Jacobian is equal to
%% \[
%% \left[ 
%% \begin{array}{cccccc}
%% \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}            &0\hdots 0&\hdots& 0 \hdots 0                                         & \hdots & 0\hdots 0 \\ 
%% \frac{\pa F_{1}}{\pa X_1}\hdots \frac{\pa F_{1}}{\pa X_n}     &0\hdots 0&\hdots& \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n} & \hdots & 0\hdots 0 \\
%% \ddots                                                        &0\hdots 0&\ddots&\ddots                                              & \ddots & \ddots \\
%% \frac{\pa F_{n-i}}{\pa X_1}\hdots \frac{\pa F_{n-i}}{\pa X_n} &0\hdots 0&\hdots&0 \hdots 0&  \hdots & \frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}  
%% \end{array}
%% \right]. 
%% \] 
Since $f$ is square-free, $I(V(f)) = \langle f \rangle.$ Therefore, for all $\xb \in V(f)$, 
\[
T_{\xb} V(f) = \textrm{Nullspace}(\grad_{\xb} f).
\]
Since $V(f)$ is smooth, $T_{\xb} V(f)$ has dimension $n-1$ and one partial vanishes. At least one partial of $f$ must be non-zero. Since  $\frac{\pa f}{\pa X_1} \hdots \frac{\pa f}{\pa X_n}$ appears in $n-i+1$ rows, the matrix has full rank $n-i+1$.
\end{proof}
%
Since $\deg \Phi_i \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Xi_i \subset \C^{n^2}$ exists, of degree at most $D^{n+(n-i+1)}=D^{2n-i+1}\leq D^{2n},$ with the property that, if $A \in \C^{n^2}-\Xi_i,$ then 
%
\[
 \jac_\xb \left(f^A,\frac{\pa f^A}{\pa X_{i+1}},\hdots,\frac{\pa f^A}{\pa X_n}\right)
\]
has full rank for all $\xb \in V(f^A)$ ($\cap \R^n$?), so that  $f^A$ satisfies $\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2)$ and $\textbf{H}_i^{'}(3)$ by the Jacobian criterion \cite[Theorem 16.19]{ECA}. Now, to prove the claim for all $i \in \{1,\hdots,n\},$ we take
\[
\Delta_1 := \bigcup_{i=1}^n \Xi_i,
\]
where we have the following bound on the degree which proves the claim:
\[
\deg \Delta_1 \leq \sum_{i=1}^n \deg \Xi_i  \leq D^{2n^2}.
\]

\section{Property ${\bf H}_i(2)$ -- Noether position}

Throughout this section, we consider that $i \in \{1,\hdots,n\}$ is
fixed. We prove that there exists a hypersurface $\D_{3,i} \subset
\C^{n^2}$ such that if $\mA$ is not in $\D_{3,i}$, then $\mA$ is
invertible and satisfies $\textbf{H}_i(1)$ and $\textbf{H}_i(2)$.

Let $\A$ be an $n \times n$ matrix of new indeterminates
$(\A_{i,j})_{1 \leq i , j \leq n}.$ Define $f^{\A} \in
\mathbb{Q}(\A)[\textbf{X}]$ as $f(\A\textbf{X})$ and $V^\A=V(f^\A).$
Recall from Section 4.1.4 that $f^\A$ satisfies
$\textbf{H}_i^{'}(1),\textbf{H}_i^{'}(2),$ and $\textbf{H}_i^{'}(3).$
, to simplify notation, let $\I^\A$ denote
$\I(\pi_i,V^\A)$ and let $W^\A$ denote $W(\pi_i,V^\A).$ Furthermore,
throughout this section, We will avoid writing $i$ where the context is clear.
%
\subsection{Sketch of the proof}
%
Let $f \in \mathbb{Q}[X_1,\hdots,X_n]$ have total degree $D$. Assume $f$ satisfies \textbf{H}, so that $f$ is squarefree with $V(f)$ smooth. Recall $\textbf{H}_i^{'}(7):$ \textit{$W(\pi_i,V)$ is in Noether position for $\pi_{i-1}$}, which is equivalent to having the extension
